Greedy Heuristics for Solving the Weighted Orthogonal Art Gallery Problem

### 2020-08-26 doc/paper.tex
minor fix
added fxnotes

          \begin{algorithm}[!t] 
          	\caption{Greedy Heuristic}\label{alg:greedy}
          	\begin{algorithmic}[1]
          		\State \textbf{Input:} an instance of a problem
          		\State \textbf{Output:} A (feasible) non-expandable solution (or reporting that no feasible solution)
          		\State $s^{P} \gets ()$ \hspace{0.3cm}// partial solution set to empty solution
          		\While{$\text{Extend}(s^{P}) \neq \emptyset$}
          		\State Select component $e \in  \text{Extend}(s^{P})$ \hspace{0.3cm}//\,w.r.t.\  some criterion
          		\State Extend $s^{P}$ by $e$
          		\EndWhile
          	\end{algorithmic}
          \end{algorithm}
      \subsection{Greedy Heuristic based on Price-per-Unit}
       Our greedy criterion to expand current partial solution $s^P$  is based on the WOAGP characteristics, that is considering not-yet-covered regions of polygon $P$, that is, its discretisation $D(P)$. For each not yet considered guards $p_i$, we assign the region he is able to see by $S_{p_i}$. As the next candidate to extend $s^P$, we choose not-yet-considered guard $p^*$ which is able to cover his part $S_{p_i}$ by smallest price per unit, among the other not considered guards. More precisely, greedy criterion $g$ is given as:
       \begin{align}
            g(s^p, p_i) = \frac{w_{p_i}}{S_{p_i}},
       \end{align}
       and $p^*$ that minimizes $g(s^p, p^*)$ value is chosen as an extension of the current partial solution.
       Afterwards the region $S_{p^*}$ is further then dropped off from $P$, i.e., $P=P \setminus S_{p^*}$, and update $s^p= s^p \cup \{p^*\}$.  These steps are repeated until $s^P$ is complete, which means $P = \emptyset$ (it is covered by the guards from $s^P$).  
        \subsection{An Alternative Greedy Heuristic}
        \fxnote{TODO}
     \section{Computational Results}

     \section{Conclusions and Future Work}

>>>>

          \begin{algorithm}[!t] 
          	\caption{Greedy Heuristic}\label{alg:greedy}
          	\begin{algorithmic}[1]
          		\State \textbf{Input:} an instance of a problem
          		\State \textbf{Output:} A (feasible) non-expandable solution (or reporting that no feasible solution)
          		\State $s^{P} \gets ()$ \hspace{0.3cm}// partial solution set to empty solution
          		\While{$\text{Extend}(s^{P}) \neq \emptyset$}
          		\State Select component $e \in  \text{Extend}(s^{P})$ \hspace{0.3cm}//\,w.r.t.\  some criterion
          		\State Extend $s^{P}$ by $e$
          		\EndWhile
          	\end{algorithmic}
          \end{algorithm}
      \subsection{Greedy Heuristic based on Price-per-Unit}
       Our greedy criterion to expand current partial solution $s^P$  is based on the WOAGP characteristics, that is considering not-yet-covered regions of polygon $P$, that is, its discretisation $D(P)$. For each not yet considered guards $p_i$, we assign the region he is able to see by $S_{p_i}$. As the next candidate to extend $s^P$, we choose not-yet-considered guard $p^*$ which is able to cover his part $S_{p_i}$ by smallest price per unit, among the other not considered guards. More precisely, greedy criterion $g$ is given as:
       \begin{align}
            g(s^p, p_i) = \frac{w_{p_i}}{S_{p_i}},
       \end{align}
       and $p^*$ that minimizes $g(s^p, p^*)$ value is chosen as an extension of the current partial solution.
       Afterwards the region $S_{p^*}$ is further then dropped off from $P$, i.e., $P=P \setminus S_{p^*}$, and update $s^p= s^p \cup \{p^*\}$.  These steps are repeated until $s^P$ is complete, which means $P = \emptyset$ (polygon $P$ is covered by the guards from $s^P$).  
        \subsection{An Alternative Greedy Heuristic}
        \fxnote{TODO: work in progress...} Greedy criterion: 
          \begin{itemize}
          	\item prefer those guards with a smaller cost $w_i$; 
          	\item If there are more guards with the smallest cost, 
          	prefer one with the largest $S_{p_i}$.
          \end{itemize}
     \section{Computational Results}
     \fxnote{to generate larger instances; practical instances...}
     \section{Conclusions and Future Work}
